FitBit Analysis

### 2023-02-13 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
update fitbit

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confident_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confident_factor = ifelse(confident_factor < 0,
                                   yes = NA,
                                   no = confident_factor),
         event = as_factor(event)
         )

@@

## Confident Factor

```{r}
df_merge %>% 
  filter(!is.na(confident_factor)) %>% 
  group_by(event, confident_factor) %>% 
  summarize(value = n()) %>% 
  mutate(prop = value/sum(value)) %>% 
  ggplot(mapping = aes(x = reorder(event, prop),
                       y = prop,
                       fill = confident_factor
                       )
         ) +
  geom_bar(position = "stack",
           stat = "identity") +
  coord_flip() +
  scale_fill_viridis_c() +
  labs(y = "",
       x = "",
       fill = "Confident Factor") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!is.na(disruption_factor) | !is.na(confident_factor)) %>% 
  ggplot(mapping = aes(x = confident_factor,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = FALSE) +
  scale_color_viridis_d() +
  labs(x = "Confident Factor",
       y = "Disruption Factor",
       color = "Event") +
  theme_apa()

@@

```{r}
df_merge %>% 
  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = confident_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Alter",
       y = "Confident Factor") +
  scale_color_viridis_d() +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_confident = mean(confident_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_confident
                       )
         ) +
  geom_point(color = "#440154") +
  geom_smooth(method = "lm",
              se = FALSE) +
  labs(x = "Alter",
       y = "Mean(Confident Factor)") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = F) +
  scale_color_viridis_d() +
  labs(x = "Alter",
       y = "Disruption Factor") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_disruption = mean(disruption_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_disruption
                       )
         ) +
  geom_point(color = "#440154") +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Alter",
       y = "Mean(Disruption Factor)") +
  theme_apa()
```

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") ->
  df_corr_pre
```

@@

- Multiple Lineare Regression
  - AV: Estimate
  - UV: Gender, Alter, Disruption Factor (mean), Confident Factor (mean)
  - Alle metrischen Variablen sind standardisiert

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") %>% 
  ungroup() ->
  df_corr_pre

left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
          gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
          ) %>% 
  pcor(., method = "spearman") %>% 
  .$estimate %>% 
  round(., 2) %>% 
  knitr::kable(format = "simple")

left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
          gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
          ) %>% 
  pcor(., method = "pearson") %>% 
  .$p.value %>% 
  round(., 3) %>% 
  knitr::kable(format = "simple")
```

@@

```{r}
left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
  ungroup() %>% 
  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = gender,
         age = (age - mean(.$age))/sd(.$age)
         ) %>%
  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m  + gender + age) %>% 
  tidy(x = .,
       conf.int = TRUE) %>% 
  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
                              term == "disruption_factor_m" ~ "Disruption Factor",
                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
                              term == "age" ~ "Alter",
                              TRUE ~ "Intercept"
                           ),
         term = fct_relevel(term, 
                            c("Confident Factor",
                              "Disruption Factor",
                              "Weiblich\n(Ref.: Männlich)",
                              "Alter"
                              )),
         term = fct_rev(as_factor(term)),
         ) %>% 
  filter(term != "Intercept") %>% 
  ggplot(mapping = aes(y = term)) +
    geom_point(aes(x = estimate)) +
  geom_vline(xintercept = 0) +
  geom_segment(mapping = aes(x = conf.low,
                             xend = conf.high,
                             y = term,
                             yend = term),
               color = "#440154") +
  labs(x = "Effect",
       y = "",
       title = "Pre-Phase",
       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
                         mean(df_corr_pre$Estimate) %>% round(.,2),
                         ")"
                         )
       ) +
  theme_apa() 
```

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") ->
  df_corr_sub

left_join(x = df_corr_sub,
          y = df_demo,
          by = "ID") %>% 
  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = gender,
         age = (age - mean(.$age))/sd(.$age)
         ) %>%
  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m + gender + age) %>% 
  tidy(x = .,
       conf.int = TRUE) %>% 
  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
                              term == "disruption_factor_m" ~ "Disruption Factor",
                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
                              term == "age" ~ "Alter",
                              TRUE ~ "Intercept"
                           ),
         term = fct_rev(as_factor(term))
         ) %>% 
  filter(term != "Intercept") %>% 
  ggplot(mapping = aes(y = term)) +
    geom_point(aes(x = estimate)) +
  geom_vline(xintercept = 0) +
  geom_segment(mapping = aes(x = conf.low,
                             xend = conf.high,
                             y = term,
                             yend = term
                             ),
               color = "#440154"
               ) +
  labs(x = "Effect",
       y = "",
       title = "Subsequent Phase",
       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
                         mean(df_corr_sub$Estimate) %>% round(.,2),
                         ")"
                         )
       ) +
  theme_apa() 
```

@@

```{r}
main %>% 
  filter(time_span == "main") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate),
            confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            age = age,
            gender = gender
            ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
         ) %>% 
  pcor()  -> pcor_main

@@

```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate),
            confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            age = age,
            gender = gender
            ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
         ) %>% 
  pcor()  -> pcor_interview

>>>>

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

@@

## confidence Factor

```{r}
df_merge %>% 
  filter(!is.na(confidence_factor)) %>% 
  group_by(event, confidence_factor) %>% 
  summarize(value = n()) %>% 
  mutate(prop = value/sum(value)) %>% 
  ggplot(mapping = aes(x = reorder(event, prop),
                       y = prop,
                       fill = confidence_factor
                       )
         ) +
  geom_bar(position = "stack",
           stat = "identity") +
  coord_flip() +
  scale_fill_viridis_c() +
  labs(y = "",
       x = "",
       fill = "confidence Factor") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!is.na(disruption_factor) | !is.na(confidence_factor)) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = FALSE) +
  scale_color_viridis_d() +
  labs(x = "confidence Factor",
       y = "Disruption Factor",
       color = "Event") +
  theme_apa()

@@

```{r}
df_merge %>% 
  filter(!is.na(confidence_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = confidence_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Alter",
       y = "confidence Factor") +
  scale_color_viridis_d() +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!(is.na(confidence_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_confidence = mean(confidence_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_confidence
                       )
         ) +
  geom_point(color = "#440154") +
  geom_smooth(method = "lm",
              se = FALSE) +
  labs(x = "Alter",
       y = "Mean(confidence Factor)") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!is.na(confidence_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = F) +
  scale_color_viridis_d() +
  labs(x = "Alter",
       y = "Disruption Factor") +
  theme_apa()
```

@@

```{r}
df_merge %>% 
  filter(!(is.na(confidence_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_disruption = mean(disruption_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_disruption
                       )
         ) +
  geom_point(color = "#440154") +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Alter",
       y = "Mean(Disruption Factor)") +
  theme_apa()
```

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") ->
  df_corr_pre
```

@@

- Multiple Lineare Regression
  - AV: Estimate
  - UV: Gender, Alter, Disruption Factor (mean), confidence Factor (mean)
  - Alle metrischen Variablen sind standardisiert

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") %>% 
  ungroup() ->
  df_corr_pre

left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
          confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
          gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
          ) %>% 
  pcor(., method = "spearman") %>% 
  .$estimate %>% 
  round(., 2) %>% 
  knitr::kable(format = "simple")

left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
          confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
          gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
          ) %>% 
  pcor(., method = "pearson") %>% 
  .$p.value %>% 
  round(., 3) %>% 
  knitr::kable(format = "simple")
```

@@

```{r}
left_join(x = df_corr_pre,
          y = df_demo,
          by = "ID") %>% 
  ungroup() %>% 
  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = gender,
         age = (age - mean(.$age))/sd(.$age)
         ) %>%
  lm(formula = Estimate ~ confidence_factor_m + disruption_factor_m  + gender + age) %>% 
  tidy(x = .,
       conf.int = TRUE) %>% 
  mutate(term = case_when(term == "confidence_factor_m" ~ "confidence Factor",
                              term == "disruption_factor_m" ~ "Disruption Factor",
                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
                              term == "age" ~ "Alter",
                              TRUE ~ "Intercept"
                           ),
         term = fct_relevel(term, 
                            c("confidence Factor",
                              "Disruption Factor",
                              "Weiblich\n(Ref.: Männlich)",
                              "Alter"
                              )),
         term = fct_rev(as_factor(term)),
         ) %>% 
  filter(term != "Intercept") %>% 
  ggplot(mapping = aes(y = term)) +
    geom_point(aes(x = estimate)) +
  geom_vline(xintercept = 0) +
  geom_segment(mapping = aes(x = conf.low,
                             xend = conf.high,
                             y = term,
                             yend = term),
               color = "#440154") +
  labs(x = "Effect",
       y = "",
       title = "Pre-Phase",
       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
                         mean(df_corr_pre$Estimate) %>% round(.,2),
                         ")"
                         )
       ) +
  theme_apa() 
```

@@

df_merge %>% 
  group_by(ID) %>% 
  summarize(confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") ->
  df_corr_sub

left_join(x = df_corr_sub,
          y = df_demo,
          by = "ID") %>% 
  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = gender,
         age = (age - mean(.$age))/sd(.$age)
         ) %>%
  lm(formula = Estimate ~ confidence_factor_m + disruption_factor_m + gender + age) %>% 
  tidy(x = .,
       conf.int = TRUE) %>% 
  mutate(term = case_when(term == "confidence_factor_m" ~ "confidence Factor",
                              term == "disruption_factor_m" ~ "Disruption Factor",
                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
                              term == "age" ~ "Alter",
                              TRUE ~ "Intercept"
                           ),
         term = fct_rev(as_factor(term))
         ) %>% 
  filter(term != "Intercept") %>% 
  ggplot(mapping = aes(y = term)) +
    geom_point(aes(x = estimate)) +
  geom_vline(xintercept = 0) +
  geom_segment(mapping = aes(x = conf.low,
                             xend = conf.high,
                             y = term,
                             yend = term
                             ),
               color = "#440154"
               ) +
  labs(x = "Effect",
       y = "",
       title = "Subsequent Phase",
       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
                         mean(df_corr_sub$Estimate) %>% round(.,2),
                         ")"
                         )
       ) +
  theme_apa() 
```

@@

```{r}
main %>% 
  filter(time_span == "main") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            age = age,
            gender = gender
            ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
         ) %>% 
  pcor()  -> pcor_main

@@

```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            age = age,
            gender = gender
            ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         gender = if_else(gender == "male",
                           true = 0,
                           false = 1),
          age = (age - mean(.$age))/sd(.$age)
         ) %>% 
  pcor()  -> pcor_interview
